---
title: "How Do Household Energy Transitions Work?"
author:
  - Jill Baumgartner (Co-PI)^1^
  - Sam Harper (Co-PI)^1^
  - Chris Barrington-Leigh^1^
  - Collin Brehmer^2^
  - Ellison M. Carter^2^
  - Xiaoying Li^2^
  - Brian E. Robinson^1^
  - Guofeng Shen^3^
  - Talia J. Sternbach^1^
  - Shu Tao^3^
  - Kaibing Xue^4^
  - Wenlu Yuan^1^
  - Xiang Zhang^1^
  - Yuanxun Zhang^4^
    
thanks: Affiliations [1] McGill Univeristy; [2] Colorado State University; [3] Peking University; [4] University of the Chinese Academy of Sciences
date: today

#format: 
# html:
#   keep-md: true

# format:
#  docx: 
#    toc: true
#    number-sections: true
#    number-depth: 3

format:
 pdf:
   toc: true
   keep-tex: true
   number-sections: true
   number-depth: 3
   include-in-header:
      - text: |
         \usepackage{wrapfig}
         \usepackage{colortbl}
          \makeatletter
          \renewenvironment{table}%
            {\renewcommand\familydefault\sfdefault
             \@float{table}}
            {\end@float}
          \renewenvironment{figure}%
            {\renewcommand\familydefault\sfdefault
             \@float{figure}}
            {\end@float}
          \makeatother
         \usepackage{changes}
         \AfterTOCHead[toc]{\sffamily}
   geometry: 
      - right=1in
      - left=1in
   fig-pos: H
bibliography: hei-report.bib
csl: environmental-health-perspectives.csl
---
```{r packages, echo=FALSE, message = FALSE, warning = FALSE}
library(here)
library(osfr)
library(tidyverse)
library(kableExtra)
library(modelsummary)
library(readxl)
library(marginaleffects)
library(tinytable)
library(tidymodels)
library(reporter)
```


```{r functions, echo=F, message=F, warning=F}
source(here("code/functions", "process-columns.R"))
```

```{r master_data, include = FALSE, cache = TRUE, echo=FALSE}
# read in master data
bhet_master_data <- osf_retrieve_node("vxur5")
bhet_master_data %>%
  osf_ls_files("Master Dataset (Seasons 1-4)",
               pattern = "csv") %>%
  osf_download(path = here("data-clean"),
               conflicts = "overwrite")
```

\newpage

# Introduction

China is deploying an ambitious policy to transition up to 70% of households in northern China from residential coal heating to electric or gas “clean” space heating, including a large-scale roll out across rural and peri-urban Beijing, referred to in this document as China’s Coal Ban and Heat Pump (CBHP) subsidy policy. To meet this target the Beijing municipal government announced a two-pronged program that designates coal-restricted areas and simultaneously offers subsidies to night-time electricity rates and for the purchase and installation of electric-powered heat pumps to replace traditional coal-heating stoves. The policy was piloted in 2015 and, starting in 2016, was rolled out on a village-by-village basis. The variability in when the policy was applied to each village allowed us to treat the roll-out of the program as a quasi-randomized intervention and evaluate its impacts on air quality and health. Household air pollution is a well-established risk factor for adverse health outcomes over the entire lifecourse, yet there is no consensus that clean energy interventions can improve these health outcomes based on evidence from randomized trials [@lai2024]. Households may be differentially affected by the CBHP due to factors such as financial constraints and user preferences, and there is uncertainty about whether and how the policy may affect indoor and outdoor air pollution, as well as heating behaviors and health outcomes.

## Subheading
### Sub-subheading


\newpage

### Personal exposure 





Table @tbl-a-het-personal shows limited evidence that the $ATT$s across cohorts and time demonstrate meaningful heterogeneity.


```{r, message = F, warning=F}
#| echo: FALSE
#| tbl-cap: Arithmetic and geometric means for air pollutant concentrations (micrograms per cubic meter) by wave.
#| label: tbl-pm-season
#| eval: TRUE

 ap_season <- read_csv(here("data-clean", 
   "ap-conc-season.csv"))


tap <- ap_season %>%
  select(-time, -substance) %>%
  pivot_longer(
    cols = Mean_S1:GM_S4,
    names_to = c("avg", ".value"),
    names_pattern = "(.*)_S(.)") %>%
  pivot_wider(
    names_from = metric,
    values_from = c(`1`, `2`, `3`, `4`)
  ) %>%
  select(-category)

colnames(tap) <- c("", "", "",  
                         "Est.", "CI", "Est.", "CI", "Est.", "CI", 
                         "Est.", "CI")
tt(tap, 
  width = c(3.5, 3, 1, 0.5, 2, 0.5, 2, 0.5, 2, 0.5, 2),
  notes = "Note: Est. = Estimate, CI = 95 percent confidence interval, GM = Geometric Mean") %>%
  format_tt(replace = "") %>%
  group_tt(
    j = list("Wave 1" = 4:5, "Wave 2" = 6:7,
      "Wave 3" = 8:9, "Wave 4" = 10:11),
    i = list("Personal measurements" = 1, 
             "Indoor measurements" = 5,
             "Outdoor measurements" = 11)) %>%
  style_tt(i = c(1, 6, 13), align = "l", bold=T) %>%
  style_tt(
    i = c(2, 4, 7, 9, 11, 14, 16, 18), j = 2, 
    rowspan = 2, alignv = "t") %>%
  style_tt(
    i = c(2, 9, 16), j = 1, rowspan = 4, alignv = "t") %>%
  style_tt(
    i = c(7, 14), j = 1, rowspan = 2, alignv = "t") %>%
  style_tt(j=1:11, fontsize = 0.8) %>%
  style_tt(i = 0, align = "c") %>%
  style_tt(i = c(3,8,10,15,17), j = 2:11, 
           line = "b", line_width = 0.1,
           line_color = "gray") %>%
  style_tt(i = c(5,12), j = 1:11, 
           line = "b", line_width = 0.1,
           line_color = "gray")

```

| |   |
|-|---|
| ANMB | 	absolute normalized mean bias |   
| ATT	 | Average Treatment Effect on the Treated | 
| BAM	 | Beta Attenuation Monitor | 
| BC	 | Black carbon | 
| BP	 | Blood pressure | 
| CI	 | Confidence Interval | 
| CIE	 | International Commission on Illumination | 
| CHP	 | Clean Heating Policy | 
| cDBP | 	Central diastolic blood pressure | 
| CRP	| C-reactive protein | 
| cSBP | 	Central systolic blood pressure | 
| DAG | 	Directed acyclic graph | 
| DiD | 	Difference-in-Differences | 
| EC | 	Elemental carbon | 
| EDXRF | 	Evo energy-dispersive X-ray fluorescence | 
| ETWFE | 	Extended Two-Way Fixed Effects | 
| FEM | 	Federal equivalent method | 
| FID | 	Flame ionization detector | 
| FeNO | 	Fractional exhaled nitric oxide | 
| HAPIN | 	Household Air Pollution Intervention Network | 
| HPLC | High-performance liquid chromatography | 
| IL-6 | 	Interleukin-6 | 
| MDA | 	Malondialdehyde | 
| NISP | 	National Improved Stove Program | 
| NIST | 	National Institute of Standards and Technology | 
| ns-S | 	Non-Sulfate Sulfur | 
| OC | 	Organic Carbon | 
| OD  | Optic densities | 
| PKU | 	Peking University | 
| PM~2.5~  | Particulate matter less than 2.5 microns in aerodynamic diameter | 
| RMSE | Root mean square error  | 
| SRM | Standard reference material | 
| TNF-$\alpha$ | Tumour necrosis factor alpha | 
| UCAS | University of Chinese Academy of Sciences | 
| UPAS | Ultrasonic Personal Aerosol Samplers | 
| W1, W2, W3, W4 | 	Wave 1, Wave 2, Wave 3, Wave 4 | 
| wi |	Water Insoluble Species | 
| ws |	Water Soluble Species | 

    
\newpage

# Abbreviations and other terms {.unnumbered}

ATT
