---
title: "How Do Household Energy Transitions Work?"
author: 
  - Sam Harper (Co-PI)
  - Jill Baumgartner (Co-PI)
date: today
# format: html
format: 
 pdf:
   toc: true
   keep-tex: true
bibliography: hei-report.bib
csl: environmental-health-perspectives.csl
---
```{r setup, echo=F, message=F}
library(here)
```

## Abstract
**Introduction**

**Methods**

**Results**

**Conclusions**

Brief summary of what we did.

## Introduction

China is deploying an ambitious plan to transition up to 70% of all households in northern China to clean space heating, including Beijing. To meet this target the Beijing municipal government announced a two-pronged program that designates coal-restricted areas and simultaneously offers subsidies to night-time electricity rates and for the purchase and installation of electric-powered, air-source heat pumps to replace traditional coal-heating stoves. The program is being rolled out on a village-by-village basis; however there is uncertainty as to when villages will receive the program. The variability in when the policy is applied to each village allows us to treat the roll-out of the program as a quasi-randomized intervention. Households may also be differentially affected by this program due to factors such as financial constraints, preferences and social capital, and there is uncertainty about whether and how this intervention may affect indoor and outdoor air pollution, as well as health behaviors and health outcomes.

## Specific Aims and Overarching Approach

This study builds on three data collection campaigns in winter 2018/19, winter 2019/20, and winter 2021/22, as well as a partial campaign in winter 2020/21 (CIHR-funded) with the following specific aims:

1. Estimate how much of the policy’s overall effect on health, including respiratory symptoms and cardiovascular outcomes (blood pressure, central hemodynamics, blood inflammatory and oxidative stress markers), can be attributed to its impact on changes in PM2.5;

2. Quantify the impact of the policy on outdoor air quality and personal air pollution exposures, and specifically the source contribution from household coal burning (Previously Aim 3);

3. Quantify the contribution of changes in the chemical composition of PM2.5 from different sources to the overall effect on health outcomes (Previously Aim 2).


## Study Design and Methods

- Field equipment
- DiD schematic
- Mediation DAG

To understand how Beijing’s policy works we used a difference-in-differences (DiD) design [@callaway2020a], leveraging the staggered rollout of the policy across multiple villages to estimate its impact on health outcomes and understand the mechanisms through which it works. Simple comparisons of treated and untreated (i.e., control) villages after the CBHP policy has been implemented are likely to be biased by unmeasured village-level characteristics (e.g., migration, average winter temperature) that are associated with health outcomes. Similarly, comparisons of only treated villages before and after exposure to the program are susceptible to bias by other factors associated with changes in outcomes over time (i.e., secular trends, impacts of the COVID-19 pandemic). By comparing *changes* in outcomes among treated villages to *changes* in outcomes among untreated villages, we can control for any unmeasured time-invariant characteristics of villages as well as any general secular trends affecting all villages that are unrelated to the policy

```{r, engine='tikz', echo=F, out.width="70%", fig.cap = "Stylized example of difference-in-differences"}
\begin{tikzpicture}
    \draw[very thin,color=gray] (0,0) (6.9,4.9);
    \draw[->] (0,0) -- (6.2,0) node[right] {};
    \draw[->] (0,0) -- (0,4.2) node[above] {$outcome$};
    \node at (1,-0.2) {Time 1};
    \node at (5,-0.2) {Time 2};
    \node at (3,-0.2) [color=gray] {Intervention};
    \draw[-, dashed, color=gray] (3,0) -- (3,4);
    \draw[-, thick, color=blue] (1,1) -- (5,2.5);
    \filldraw[color=blue] (1,1) circle(0.8mm);
    \filldraw[color=blue] (5,2.5) circle(0.8mm);
    \node at(4.1,1.5) [color=blue] {\small{Control}};
    \node at(4.1,1.1) [color=blue] {\small{group}};
    \draw[-, thick, color=red] (1,2.5) -- (3,3.25);
    \draw[-, thick, dashed, color=red!50] (3,3.25) -- (5,4);
    \draw[-, thick, color=red] (3,3.25) -- (5,3.4);
    \filldraw[color=red] (1,2.5) circle(0.8mm);
    \filldraw[color=red!50] (5,4) circle(0.8mm);
    \filldraw[color=red] (3,3.25) circle(0.8mm);
    \filldraw[color=red] (5,3.4) circle(0.8mm);
    \node at(1.5,3.25) [color=red] {\small{Treated group}};
\end{tikzpicture}
```

The DiD design compares outcomes before and after an intervention in a treated group relative to the same outcomes measured in a control group. The control group trend provides the crucial "counterfactual" estimate of what would have happened in the treated group had it not been treated. By comparing each group to itself, this approach helps to control for both measured and unmeasured fixed differences between the treated and control groups. By measuring changes over time in outcomes in the control group unaffected by the treatment, this approach also controls for any unmeasured factors affecting outcome trends in both treated and control groups. This is important since there are often many potential factors affecting outcome trends that cannot be disentangled from the policy if one only studies the treated group (as in a traditional pre-post design).

The canonical DiD design [@card1994] compares two groups (treated and control) at two different time periods (pre- and post-intervention, Figure X). In the first time period both groups are untreated, and in the second time period one group is exposed to the intervention. If we assume that the differences between the groups would have remained constant in the absence of the intervention (parallel trends assumption), then an unbiased estimate of the impact of the intervention in the post period can be calculated by subtracting the pre-post difference in the untreated group from the pre-post difference in the treated group. 

However, when multiple groups are treated at different time periods, the most common approach has been to use a two-way fixed effects model to estimate the impact of the intervention which controls for secular trends and differences between districts. However, recent evidence suggests that the traditional two-way fixed effects estimation of the treatment effect may be biased in the context of heterogeneous treatment effects [@callaway2021;@goodman-bacon2021a]


## Data Analysis

### Total Effect
To estimate the total effect of the policy we used a DiD analysis that accommodates staggered treatment rollout. To allow for heterogeneity in the context of staggered rollout we used 'extended' two-way fixed effects (ETWFE) models [@wooldridge2021a] to estimate the total effect of the CBHP policy. The mean outcome (replaced by a suitable link function $g(\cdot)$ for binary or count outcomes) was defined using a set of linear predictors:

$$Y_{ijt}=g(\mu_{ijt}) = \alpha + \sum_{r=q}^{T} \beta_{r} d_{r} + \sum_{s=r}^{T} \gamma_{s} fs_{t}+ \sum_{r=q}^{T} \sum_{s=r}^{T} \tau_{rt} (d_{r} \times fs_{t}) + \varepsilon_{ijt}$$ {#eq-etwfe}

where $Y_{ijt}$ is the outcome for individual $i$ in village $j$ at time $t$, $d_{r}$ represent fixed effects for cohorts of villages that were exposed to the policy at the same time (e.g., in 2019, 2020, or 2021), $fs_{t}$ are time fixed effects corresponding to different winter data collection campaigns (2018-19, 2019-20, or 2021-22), and $\tau_{rt}$ are the cohort-time *ATTs*.

### Mediation Analysis
As noted above, with respect to the mediation analysis we are chiefly interested in the $CDE$, which can be derived by adding relevant mediators $M$ to this model. If we also allow for exposure-mediator interaction and potentially allow for adjustment for confounders $W$ of the mediator-outcome effect, we can extend equation {#eq-etwfe} as follows:

$$Y_{ijt}=g(\mu_{ijt}) = \alpha + \sum_{r=q}^{T} \beta_{r} d_{r} + \sum_{s=r}^{T} \gamma_{s} fs_{t}+ \sum_{r=q}^{T} \sum_{s=r}^{T} \tau_{rt} (d_{r} \times fs_{t}) \\ + \delta M_{it} + \sum_{r=q}^{T} \sum_{s=r}^{T} \eta_{rt} (d_{r} \times fs_{t} \times M_{it}) + \zeta \mathbf{W} + \varepsilon_{ijt}$$ {#eq-etwfem}


To conduct the causal mediation analysis we represent the total effect with the following equation, noting that we simplify the DiD equation for the total effect above by dropping the error terms and using the vector $\mathbf{X}$ as a generic term to capture the cohort fixed effects ($V_{j}$), time fixed effects ($P{j}$) and other covariates ($Z_{jt}$ and $X_{ijt}$) that, as noted above, we assume are sufficient to estimate the total effect: 

$$E[Y|T,X]=\beta_{0}+\beta_{1}T +\beta_{2}\mathbf{X}$$

where $\beta_{1}$ represents the impact of the intervention $T$ and $X$ represents a vector of pre-treatment covariates sufficient to estimate the total effect without bias. After estimating the total effect, we will estimate the controlled direct effect ($CDE$), which gives the effect of the intervention on outcomes through pathways other than the proposed mediator (i.e., the “direct” path $T\rightarrow Y$ in the DAG (Figure ?) above), after setting the mediator to a specific value. The $CDE$ can be derived after estimating the following equation: 


$$E[Y|T,X,M] = \gamma_{0} + \gamma_{1}T + \gamma_{2}M + \gamma_{3}TM + \gamma_{4}X + \gamma_{5}W$$

Noting that $\gamma_{3}$ allows for interaction between the exposure and mediator, the $CDE$ is estimated as: $\gamma_{1}+\gamma_{3}MT$. In the absence of interaction between the exposure and the mediator (i.e., $\gamma_{3}=0$) the $CDE$ will simply be $\gamma_{1}$, i.e., the effect of the policy holding $M$ constant. For a valid estimate of the $CDE$ we must account for confounding of the mediator-outcome effect, represented by $W$ in the equation above. In our example this might include changes in cooking behavior, diet or tobacco smoking, or indoor temperature. Baseline measures of both the outcome and the proposed mediators will help to reduce the potential for unmeasured confounding of the mediator-outcome effect [@Keele:2015aa]. In addition to estimating the $CDE$, we may also be interested in measures of how much of the of the policy’s impact may be due to its impact on the mediator. One potential way of estimating this is to subtract the $CDE$ from the $TE$ and express this as a proportion (sometimes called the “proportion eliminated”), i.e., $PE = [TE - CDE(m)] / TE$ or, using the two equations above, $(\beta_{1} - \gamma_{1}) /  \beta_{1}$. In our example this corresponds to the proportion of the total effect of the CBHP policy on blood pressure that could be eliminated if we were to fix PM~2.5~ at a certain value $M=m$.

## Results

### Description of study sample (Table)

- Study flowchart of participants (Figure)
- Description of PM measurements (Figure)
- Uptake of the policy (Sankey energy use Figure)
- Impact of ‘treatment assignment’ on coal use (Figure? Table?)

### Aim 1

- Impact of policy on PM mass (Figure)
- Table of CDEs (Central SBP, Central DBP, FeNO, Respiratory outcomes, inflammatory markers), mediated by indoor PM (CDEs for personal and outdoor in SI)
- Table for multiple mediation analysis for BP

### Aim 2 (was Aim3)

- Figure of source contributions (6 or fewer components)
- Source contributions by treatment status
- DiD for source contributions to PM

### Aim 3
- Table of mediated health effects by source contribution (coal and biomass)


## Discussion and Conclusions

Other relevant results (Tables or figures in SI)
- Temperature
- Heating room
- Well-being


## Implications of Findings
To come... 


## Data Availability Statement
To come... 


## Acknowledgements
To come... 


## References

::: {#refs}
:::

## Appendices

## About the authors

## Other publications

Other papers that have been published.[@li2022;@li2022a;@sternbach2022]
